EvoSuite at the SBST 2017 Tool Competition

### 2017-02-21 papers/sbst17/paper_sbst17.tex
on vagueness

% Look at benchmarks where coverage decreased with increased budget
Although coverage generally increased with higher time budgets, there
are instances where this expected behaviour was not observed,
specially for $budget=300s$, where the average across benchmarks
decreased. This is possibly due to crashes or out-of-memory runtime
errors. For instance, \EVOSUITE failed to generate any test suite in
one out of three runs of OKHTTP-2 and RE2J-7 due to an
\textit{out-of-memory error}, and in all executions of LA4J-3 and
LA4J-7 due to a \textit{state exception}. In order to evaluate a
fitness function, each test case evolved by the underline GA of
\EVOSUITE has to be executed. However, its execution could fail due to
several reasons: state exception (if a test case tries to re-initalize
EvoSuite's sanbox, LA4J-3 and LA4J-7), timeout (OKHTTP-2), etc. In
case of a timeout, \EVOSUITE logs the stacktrace of the thread in
which each test case is executed, which could cause an out-of-memory
error if the stack trace message is to long. RE2J-7: \TODO{I do not
understand how a java.lang.OutOfMemoryError could be throw by
CBranchSuiteFitness.java:145}.
%
To avoid low coverage of final classes with private constructors (like
the class under test of benchmark OKHTTP-7), \EVOSUITE uses reflection
to call the default constructor of the class under test. However,
\TODO{EvoSuite tries to access a field of the cut (which is public
static final) by using an instance of cut. It's still not clear why}.
For other benchmarks such for example BCEL-1, BCEL-5, BCEL-7,
\EVOSUITE failed due to mocking related issues.

@@

% Mocking
As mentioned in the previous section, \EVOSUITE now uses private
API access and functional mocking%  in addition to environment
% mocking
~\cite{ICST_Mocking17}. In the competition, a total of 20,921
objects were mocked, 1,485 private fields were set and 3,090 private methods
were invoked using mocked access% , and environment classes were
% mocked 4,699 times, with \texttt{java.util.Random} and
% \texttt{java.io.File} being by far the most frequently mocked
% environment classes (resp. 1,286 and 1,121 times)
. Further
investigation is needed to assess the impact of these mocking features
on test generation effectiveness for the benchmarks in the competition.

>>>>

% Look at benchmarks where coverage decreased with increased budget
As expected, both branch coverage and mutation score generally
increased with higher time budgets, although in some cases, specially
at $budget=300s$, a decrease was observed for some benchmarks. Having
run only three repetitions of the tool per time budget, it is fair to
assume the decreases are due to bugs affecting executions with
$budget=300s$ by chance. A preliminary investigation on the source of
this loss of coverage revealed that out-of-memory errors (e.g., for
OKHTTP-2 and RE2J-7), sandboxing problems (e.g., for LA4J-3 and
LA4J-7), and mocking-related issues (e.g., for BCEL-1, BCEL-5, BCEL-7)
are some of the problems in \EVOSUITE.

% Although coverage generally increased with higher time budgets, there
% are instances where this expected behaviour was not observed,
% specially for $budget=300s$, where the average across benchmarks
% decreased. This is possibly due to crashes or out-of-memory runtime
% errors. For instance, \EVOSUITE failed to generate any test suite in
% one out of three runs of OKHTTP-2 and RE2J-7 due to an
% \textit{out-of-memory error}, and in all executions of LA4J-3 and
% LA4J-7 due to a \textit{state exception}. In order to evaluate a
% fitness function, each test case evolved by the underline GA of
% \EVOSUITE has to be executed. However, its execution could fail due to
% several reasons: state exception (if a test case tries to re-initalize
% EvoSuite's sanbox, LA4J-3 and LA4J-7), timeout (OKHTTP-2), etc. In
% case of a timeout, \EVOSUITE logs the stacktrace of the thread in
% which each test case is executed, which could cause an out-of-memory
% error if the stack trace message is to long. RE2J-7: \TODO{I do not
% understand how a java.lang.OutOfMemoryError could be throw by
% CBranchSuiteFitness.java:145}.
% %
% To avoid low coverage of final classes with private constructors (like
% the class under test of benchmark OKHTTP-7), \EVOSUITE uses reflection
% to call the default constructor of the class under test. However,
% \TODO{EvoSuite tries to access a field of the cut (which is public
% static final) by using an instance of cut. It's still not clear why}.
% For other benchmarks such for example BCEL-1, BCEL-5, BCEL-7,
% \EVOSUITE failed due to mocking related issues.

@@

% Mocking
As mentioned in the previous section, \EVOSUITE now uses private
API access and functional mocking%  in addition to environment
% mocking
~\cite{ICST_Mocking17}. In the competition, a total of 20,921
objects were mocked, 1,485 private fields were set and 3,090 private methods
were invoked using mocked access% , and environment classes were
% mocked 4,699 times, with \texttt{java.util.Random} and
% \texttt{java.io.File} being by far the most frequently mocked
% environment classes (resp. 1,286 and 1,121 times)
, adding up to represent only 1.09\% of the total number of lines of code
in the \EVOSUITE-generated test suites (2,329,361 LOC). Further
investigation is needed to assess the impact of these mocking features
on test generation effectiveness for the benchmarks in the
competition.
